The \emph{TestIdeals} package for \emph{Macaulay2}

### 2019-06-11 Fsing/TestIdealsPaper/TestIdeals.tex
Fixed a typo in the TestIdeals paper.
Cleaned up that typo in the TestIdeals paper further.
Added new acknolwedgements to the TestIdeals paper.

\subsection*{Acknowledgements}
The authors thank other contributors of the \emph{TestIdeals} package, namely
Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.
This paper, and the finishing touches to the \emph{TestIdeals} package, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.  The authors also thank the referees for their numerous useful comments on both this paper and the code.

@@

After the test element $c$ has been identified, we pull back the ideal $\omega_R$ to an ideal $J \subseteq S$.  Next, we compute the following ascending sequence of ideals:
\begin{equation}
\label{eq.AscendIdealExplanation}
\begin{array}{lll}
J_1 &\colonequals   J + (c J)^{[1/p]} & \\
J_2 &\colonequals   J_1 + (c J_1)^{[1/p]} & = J + (c J)^{[1/p]} + (c^{1+p} J)^{[1/p^2]} \\
J_3 &\colonequals    J_2 + (cJ_2)^{[1/p]} & = J + (c J)^{[1/p]} + (c^{1+p} J)^{[1/p^2]} + (c^{1+p+p^2} J)^{[1/p^3]} \\
\vdots
\end{array}
\end{equation}
As soon as this ascending sequence of ideals stabilizes, we are done.
In fact, because this strategy is used in several contexts, the user can call it directly for a chosen ideal $J$ and $u$ with the function \texttt{ascendIdeal} (this is done for test ideals below).

>>>>

\subsection*{Acknowledgements}
The authors thank other contributors of the \emph{TestIdeals} package, namely
Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.  We also thank Thomas Polstra for pointing out typos in a previous version of this paper.
This paper, and the finishing touches to the \emph{TestIdeals} package, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.  The authors also thank the referees for their numerous useful comments on both this paper and the code.  Additional work on the package was also done at the Institute of Mathematics and its Applications for its generous support for a 2019 Coding Sprint on the \emph{FThresholds} package.

@@

After the test element $c$ has been identified, we pull back the ideal $\omega_R$ to an ideal $J \subseteq S$.  Next, we compute the following ascending sequence of ideals where $u$ represents $T:\omega_{R^{1/p^e}} \to \omega_R$ as above:
\begin{equation}
{\arraycolsep=1.4pt
\label{eq.AscendIdealExplanation}
\begin{array}{lll}
J_0 & \colonequals  cJ \\
J_1 &\colonequals   J_0 + (u J_0)^{[1/p]} & \\
J_2 &\colonequals   J_1 + (u J_1)^{[1/p]} & = J_0 + (u J_0)^{[1/p]} + (u^{1+p} J_0)^{[1/p^2]} \\
J_3 &\colonequals    J_2 + (uJ_2)^{[1/p]} & = J_0 + (u J_0)^{[1/p]} + (u^{1+p} J_0)^{[1/p^2]} + (u^{1+p+p^2} J_0)^{[1/p^3]} \\
\vdots
\end{array}
}
\end{equation}
As soon as this ascending sequence of ideals stabilizes, we are done.
In fact, because this strategy is used in several contexts, the user can call it directly for a chosen ideal $J$ and $u$ with the function \texttt{ascendIdeal} (this is done for test ideals below).
